\papertitle

### 2021-03-05 source_separation/paper/paper.tex
add short description to demucs and open-unmix

			\subsubsection{Demucs}
			@Leo/Alejandro

			Demucs \cite{demucs}

			\subsubsection{OpenUnmix}
			@Leo/Alejandro

			OpenUnmix \cite{open-unmix}

>>>>

			\subsubsection{Demucs}
			The Demucs~\cite{demucs} architecture is a deep learning model for musical source separation. It takes as input the stereo mixture, and outputs 4 stereo waveforms corresponding to the stems (vocals, bass, drums and others). Demucs is based on a convolutional encoder, a bidirectional LSTM and a convolutional decoder. The encoder and the decoder are linked with skip U-Net connections. Both the encoder and the decoder are made of 6  blocks, each made of a combination of a convolutional layer with kernel size 8 followed by ReLU activation and a convolution with kernel size 1 followed by gated linear units (GLU). The U-network structure allows the decoder to directly access the input signal and to transfer its phase, improving results.

			\subsubsection{OpenUnmix}
			Open-Unmix~\cite{open-unmix} is based on a bidirectional LSTM model from~\cite{Uhlich2017}. It is an open-source implementation of a musical source separation system. It takes as input the Short-Time Fourier Transform of the input signal.
